% !TEX root = ../main.tex

\chapter{Characteristics}
\label{sec:characteristics}
\section{Overview}
All models have a listing of values known as a Characteristics
Profile. The profile differs between Vehicle Models and Non-
Vehicle Models. This section is only concerned with the
Characteristics of Non-Vehicle Models.

All Characteristics are measured from 0 - 10, where higher is better
except for Saves. Models with a Zero Level Characteristic may not
test this Characteristic.


\section{The Characteristics Profile}
The Characteristics Profile looks like this:

\begin{tblr}{
	colsep = 0pt,
	width = \linewidth,
	colspec = {X[3,l] X[1,c] X[1,c] X[1,c] X[1,c] X[1,c] X[1,c] X[1,c] X[1,c] X[1,c] X[1,c]}
	% columns = {1.875em, c},
	% column{1} = {c}
	}
 & {\bfseries WS}  & {\bfseries BS}  & {\bfseries S} & {\bfseries T} & {\bfseries W} & {\bfseries I} & {\bfseries A} & {\bfseries Ld} & {\bfseries Sv} \\
Space Marine & 4 & 4 & 4 & 4 & 1 & 4 & 2 & 8 & 3+  \\
\end{tblr}

\section{The Characteristics in Detail}

Here's a quick summary to what it stands for:

\subsection{Weapon Skill (WS)}
Skill in close combat. A Normal Human has WS3.

\subsection{Ballistic Skill (BS)}
Accuracy with ranged attacks. A Normal Human has BS3.

\subsection{Strength (S)}
How hard an attack from this model hits. A Normal Human has S3.

\subsection{Toughness (T)}
The higher this Characteristic, the better it can survive shots or

blows. A Normal Human has T3.
\subsection{Wounds (W)}
How much damage a model can take before it can no longer fight.

A Normal Human has W1.
\subsection{Initiative (I)}
Used in close combat to determine which models strike first. A

Normal Human has I3.
\subsection{Attacks (A)}
The normal number of attacks a model makes during close combat.

A Normal Human has A1.
\subsection{Leadership (Ld)}
Used in a Leadership Test, typically concerns Morale and Directed

Fire. Tested by rolling 2D6, succeeding if the result is less than the
Characteristic of the model. A Normal Human has Ld7.
\subsection{Save (Sv)}

The chance to avoid damage when struck or shot, based on armor
or natural defenses like chitinous hide. When tested, the roll is a
success when the face value of the die is equal or greater to the
Characteristic. A Normal Human has Sv 5+.


\section{Unlisted}
Every models have three more values that won’t appear on a
Characteristics Profile:

\section{Movement}
All models move 6” unless otherwise specified.

\section{Type}
For the purposes of any special rules, such as Jump Infantry or
Monstrous Creatures.

\section{Point Value}
The cost to include this model in an Army List for a game of
Warhammer 40,000 4th Edition.

