% !TEX root = ../main.tex


\chapter{Introduction}

\section{Overview}

The sections on Characteristics, The Turn, The Movement Phase,
The Shooting Phase, The Assault Phase and Morale contain all the
basic rules you need to play (the Core Rules).

Additional sections on Characters, Unit Types, a Universal Special
Rules directory, Force Organization, and Missions add additional
detail to the game and round out the Complete Rules.

Sections on Special Missions, Battle Missions, Raid Missions,
Breakthrough Missions, Campaigns, Combat Patrols, and Kill
Teams add additional content in the form of Supplementary Rules,
however have not been included in this document as they exceed
the scope.

\section{The Most Important Rule}
Have fun while playing, and try to ensure the other player(s) are
also having fun by being an agreeable opponent.

\section{Required Materials}
The following will be required to play a game of Warhammer
40,000 4th Edition:

\begin{itemize}[label={--}]
	\item The Core Rules (optionally: the Complete Rules)
	\item Two or more players
	\item A selection of miniatures for all players
	\item A firm, level surface to play on, ideally 6’ x 4’ in size
	\item A selection of terrain, such as hills, walls, ruined buildings,
wreckage, jungle or woods
	\item The relevant Codex books for the miniatures in use
	\item A measuring device, such as a ruler or retractable tape measure
marked in inches
	\item Six-sided dice, 20 should suffice, and optionally a Scatter Die
	\item A pen and paper for record keeping
	\item A set of flamer, Blast, and Large Blast templates
\end{itemize}


\section{Dice Rolls}
All dice rolls in Warhammer 40,000 use a standard six-sided die
(“d6” henceforth).

\subsection{Roll d6}
Roll d6 and compare the face value to the target number.

\subsection{Roll Xd6}
Roll a number of d6 equal to X and sum the values to obtain the
result.

\subsection{Roll d6X}
Roll a d6, then multiply the face value by X to obtain the result.


\subsection{Roll d3}
Roll a d6, then divide by 2. Round this result up to the nearest
whole number to obtain the result.


\subsection{Alternate Scatter dice}
If you don't have a scatter dice, take a sharpy marker and make one using any plain dice, using two opposing direct hits, and four arrows.

\subsection{Re-rolls}
When a rule calls for a re-roll, pick up the d6 to be re-rolled and
roll them again. The new face value is always the final result, even
if it is worse than the first. No single die can be re-rolled more than
once regardless of the source of the re-roll.



