% !TEX root = ../main.tex

\chapter{Models}


\section{Overview}
The miniatures used to play the game are referred to as models in
the rules text. Each model is an individual playing piece with its
own capabilities. When the term ``model'' is used in the rules it
applies to both Non-Vehicle and Vehicle models. If the term ``Non-
Vehicle Model'' is used the rule only applies to Non-Vehicle
Models, and likewise for Vehicle Models.

Model base \& height guidelines are conventions that affect all
models used in a game of Warhammer 40,000 4th Edition.

\section{Non-Vehicles \& Vehicles}
Non-vehicle models are the most common in the game and use a
standard profile as described in the Characteristics Section (see page \pageref{sec:characteristics}).

\subsection{Vehicle Models}
Includes all vehicles that enclose the crew. Small vehicles such as
Bikes are not included and are dealt with as Non-Vehicle Models.

\section{Model Basing Guidelines}

Non-Vehicle Models on bases occupy the area of their base for the
purpose of all rules, even if limbs or other elements overhang.
Vehicle Models and Non-Vehicle Models that have no base use the
area occupied by the model's main body or hull instead.

Citadel miniatures come with bases that are to be used with the
model, if using proxy miniatures attempt to match the base size for
the model you are proxying. Having a reasonably larger than
normal base is acceptable, but a smaller than normal base for the
model is not. Here's the suggested list:


\subsection{Infantry}
25 - 32mm

\subsection{Heavy or Larger Infantry}
40-50mm

\subsection{Walkers, Monstrous Creatures}
64 - 80mm

\subsection{Bike, Jetbikes, Cavalry}
90mm oval base, or 40mm round on post.

\subsection{Vehicles}
None required, fitting the hull if needed.

There are three broad height bands into which all models fall.
These height bands also are used to define terrain features. Height
is only used during the Shooting Phase when determining Line of
Sight and Target Priority.

\subsection{Size 1}
Used for a selection of miniatures deemed significantly smaller
than standard for models.

\subsection{Size 2}
Standard Targets, every model not indicated to be in either of the
other two categories.

\subsection{Size 3}
Used for Monstrous Creatures and Vehicles.
