% !TEX root = ../main.tex

\chapter{The Turn}


\section{Overview}
During the course of a game of Warhammer 40,000 4th Edition
players alternate taking turns moving and fighting with their Units.
During a Turn the player can move and fight with all his units if he
wishes. The actions of moving, shooting, and fighting are dealt with
one after another.

\section{The Battle Round}
During each Battle Round of a game of Warhammer 40,000 4th
Edition each player gets a Turn and performs their actions in each
Phase –- Movement, Shooting, and Assault.

There are as many Turns in a Battle Round as there are players. All
players roll a d6 at the start of the Battle Round and complete their
Turns in descending order.


\section{The Turn Summary}
A Turn is comprised of the following three distinct phases:

\subsection{1) Movement Phase}
The player can move any of his Units eligible to do so.

\subsection{2) Shooting Phase}
The player can shoot with any of his Units eligible to do so.

\subsection{3) Assaulting Phase}
The player can move any of his Units to assault enemies that are
close enough to do so, fighting in close combat. Both forces fight
during the Assault Phase but only the player with the active turn
can move into an Assault.

\section{Ending the Game}
Most games have a limit of six Battle Rounds. However in some
Mission Types a player might be able to achieve a victory condition
that ends the game immediately. Alternatively a game may be D6
Battle Rounds long, or end when one player concedes, or after a set
time has elapsed.

Mission Types will be used for the purposes of Scoring to
determine a winner and may be read in detail on page \pageref{sec:missions}.
